---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Neattools

<!-- badges: start -->
<!-- badges: end -->

The goal of neattools is to make certain data frame manipulations easier.

## Installation

You can install the development version of neattools from [GitHub](https://github.com/) with:

``` {r}
# install.packages("devtools")
#devtools::install_github("timovoskuilen/neattools")
library(neattools)
```

## Functions

This package includes 4 functions, which will all be shown including examples below.

The function __flip__ flips the columns and rows from a dataframe:
```{r, message = FALSE}
head(mtcars, n = 2)
flip(head(mtcars, n = 2))
```

the function __ removecolumn__ lets you remove a specific column from a dataframe
```{r, message = FALSE}
head(layout, n = 2)
removecolumn(head(layout, n =2), "Drug")
```

the function __subset__ lets you subset specific rows from a  dataframe
```{r, message = FALSE}
head(layout, n = 2)
subset(head(layout, n = 2), 1)
```

the function __replacevalue__ lets you replace a specific value in a dataframe
```{r, message = FALSE}
head(layout, n = 5)
replacevalue(head(layout, n = 5), "Drug", "Analyfyn", "Test")
```
## Data

### layout
A dataset containing a made up 384 well plate layout for drug screening.

## Credits

Functions were written by Timo Voskuilen
