---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Neattools

<!-- badges: start -->
<!-- badges: end -->

The goal of neattools is to make certain data frame manipulations easier.

## Installation

You can install the development version of neattools from [GitHub](https://github.com/) with:

``` {r}
# install.packages("devtools")
#devtools::install_github("timovoskuilen/neattools")
```

## Functions

This package includes 4 functions, which will all be shown including examples below.

__Flip__: flips the columns and rows from a dataframe

```{r example}
library(neattools)
head(mtcars, n = 2)
flip(head(mtcars, n = 2))
```

__removecolumn__: removes a specific column from a dataframe
```{r}
library(tidyverse)
layout
removecolumn(layout, "Drug")

```

__subset__: lets you subset specific rows from a data frame
```{r, out.height="60%", out.width="60%"}
subset(layout, 6)
```

__replacevalue__: lets you replace a specific value in a dataframe with a user defined value
```{r, out.height="60%", out.width="60%"}
layout
replacevalue(layout, 'Drug', "Analyfyn", "test")
```

## Credits

Functions were written by Timo Voskuilen
