---
title: "neattools-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{neattools-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, message = FALSE}
library(neattools)
library(tidyverse)
```

## Neattools is a package created to prove Timo Voskuilen's ability to create packages. 

The package contrians 4 functions that make manipulating a dataframe in R easier.

Here I will give a demonstration to what the functions in this package do:

```{r, message = FALSE}
#load the made up data from a drug screening experiment.
data("layout")
```

The function __flip__ flips the columns and rows from a dataframe:
```{r, message = FALSE}
head(mtcars, n = 2)
flip(head(mtcars, n = 2))
```

the function __ removecolumn__ lets you remove a specific column from a dataframe
```{r, message = FALSE}
head(layout, n = 2)
removecolumn(head(layout, n =2), "Drug")
```

the function __subset__ lets you subset specific rows from a  dataframe
```{r, message = FALSE}
head(layout, n = 2)
subset(head(layout, n = 2), 1)
```

the function __replacevalue__ lets you replace a specific value in a dataframe
```{r, message = FALSE}
head(layout, n = 5)
replacevalue(head(layout, n = 5), "Drug", "Analyfyn", "Test")
```

